\plaintitle

### 2016-09-20 drafts/labor/relationships.tex
relationships expanded

\subsubsection[the relationships of workers]{The Relationships of Workers to Work, Peers, and Others}
\label{sec:relationships}

\subsubsubsection{\crowdworkpers}
\topic{The relationships of workers with their work, with their peers, and with others
are complex and not especially well--understood.}
Researchers have begun to appreciate
the sociality of crowd workers in labor markets
\cite{crowdcollab}.
Still, the study of these communities is made more challenging by
the limited access to workers on these sites of work
inherent to digital spaces made without social affordances
\cite{miller2011understanding}.
% Nevertheless, a number of interesting findings have
% already emerged in the crowd work literature%
% , which we can report here.
We can break this general body of work into the three groups we named earlier:
workers' relationships
\begin{inlinelist}
\item with \nameref{ch:workRelationship},
\item with \textit{requesters}, and
\item with \textit{other workers}.
\end{inlinelist}
We'll look at workers' relationships with work itself, which we'll discover
gives us insight into why people engage in crowd work in the first place.

\paragraph[relationships to work]{Relationships to work}\label{ch:workRelationship}
\topic{A number of ethical questions surrounding the
increasing complexity of crowd work have arisen in recent years.}
\citeauthor{professionalcrowdworkEthics} bring some of these issues to light
--- working for increasing amounts of time on tasks of growing complexity%
, only to discover that requesters are not willing to pay%
, for instance ---
but these and other dangers range an enormous landscape
\cite{professionalcrowdworkEthics}.
\citeauthor{crowdworkFuture}
list a few of the problems they identified in \citeyear{crowdworkFuture}
--- motivation, feedback, reputation, quality control, to name a few ---
while others discuss challenges such as fostering collective action
and the opportunity for learning and career advancement
\cite{crowdworkFuture,nickerson2013crowd,dynamo}.

Some research already looks at research such as investing in workers, and
informally, we know that this happens among industry requesters
\cite{jonBrelig,shepherdingDow}.
AMT, meanwhile, offers requesters the ability to create tasks which are
not just hidden from unqualified workers by default, but completely.
Requesters have taken to using lists of worker IDs which reference
workers who have proven their reliability,
representing a sort of proto--organization of loosely connected workers.

\subsubsubsection{\pieceworkpers}
The rise of labor unions in the \nth{20} century seems to have been precipitated by
egregiously unjust conditions imposed on workers in factories and elsewhere
\cite{ebbinghaus1999institutions}.
Incidents broadly describing this dynamic can be found in research on AMT
\cite{turkopticon,dynamo}.
If these are prototypical labor advocacy organizations of contemporary on--demand work,
the next question we should look to is if
--- and indeed \textit{how} ---
these institutions might face challenges in the future.

For insight on this, we return to \citeyear{levi2009union}'s study of labor unions,
and identify that
``Scholars who evaluate union governance by procedural criteria generally find that oligarchy tends to arise and persist even when democratic procedures are in place''
\cite{levi2009union}.
Indeed, \citeauthor{levi2009union} writes about the general perception that labor unions were either
This perception already appears to be emerging in digitally mediated peer--governed organizations,
as \citeauthor{keegan2010egalitarians} and others have illustratively documented
\cite{beschastnikh2008wikipedian,keegan2010egalitarians}.
If these organizations and others are to avoid the same fate that labor unions faced,
they should take care to study this phenomenon and attempt to avoid it.

\subsubsubsection{\whatchanged}
\topic{While online and distributed workers can be harder to find,
other features make the study thereof rewarding for the substantively different ways
that we can approach their study.}
The longitudinal analysis of everyday discourse, for instance,
is trivial in the study of online communities

@@

>>>>

\subsubsection[What will work and the place of work look like for workers]{The Relationships of Workers to Work, Peers, and Others}
\label{sec:relationships}

\subsubsubsection{\crowdworkpers}
\topic{The relationships of workers with their work, with their peers, and with others
are complex and not especially well--understood.}
Researchers have begun to appreciate
the sociality of crowd workers in labor markets
\cite{crowdcollab}.
Still, the study of these communities is made more challenging by
the limited access to workers on these sites of work
inherent to digital spaces made without social affordances
\cite{miller2011understanding}.
% Nevertheless, a number of interesting findings have
% already emerged in the crowd work literature%
% , which we can report here.
We can break this general body of work into the three groups we named earlier:
workers' relationships
\begin{inlinelist}
% \item with \textit{work}, % \nameref{ch:workRelationship},
\item with \textit{requesters}, and
\item with \textit{other workers}.
\end{inlinelist}
We'll look at workers' relationships with work itself, which we'll discover
gives us insight into why people engage in crowd work in the first place.

\topic{\ali{some topic sentence that brings together the debate where
one side blames Turkers for being bad at Turking and
another side blames requesters for not understanding Turkers as a culture of people.}}
Early on, \citeauthor{turkopticon} highlighted
the information asymmetry between workers and requesters on AMT,
leading to the creation of \textit{Turkopticon}, a site which allows
Turkers to rate and review requesters
\cite{turkopticon}.
\citeauthor{dynamo} took this critique on information asymmetry and power imbalances a step further,
% pointing out the frustration workers experience trying
designing \textit{Dynamo} to facilitate
Turkers acting collectively to bring about changes to their circumstances
--- this led to the Academic Requester Guidelines
\cite{dynamo}.
\citeauthor{fixingChaos} has since identified the chaos inherent to ``Turking'',
the unbridled power requesters have, and
the distress this causes for workers,
calling for a solution

some research frames this tension as the turker's problem
(see \citeauthor{MaliciousCrowdworkersGadiraju}),
but some has taken a more even--handed view (\citeauthor{takingAHITMcInnis})
\cite{turkopticon,dynamo,MaliciousCrowdworkersGadiraju,takingAHITMcInnis}.

\topic{}
\citeauthor{dynamo} specifically points out the ``mega--drama'' among workers;
\citeauthor{irani2015cultural} and \citeauthor{storiesIraniSilberman} discuss
the culture of crowd work and the study thereof.
\citeauthor{crowdcollab} quantifies and maps this social network of turkers
(this is different from the requesters topic because
researchers like Irani, Gray, etc\dots~aren't Turkers, but are as close to
``cultural anthropologists doing ethnography'' as we see on AMT, maybe online in general)
\cite{dynamo,irani2015cultural,storiesIraniSilberman,crowdcollab}.
% \end{enumerate}

\subsubsubsection{\pieceworkpers}
% \begin{enumerate}
  how do workers relate to work?
  %       \citeauthor{riisOtherSideLives} documents this to some extent,
  %       but doesn't say that much about interviews or anything like that.
  %       a handful of sources suggest to know something about
  %       how workers relate to the work, like \citeauthor{clark1908cotton},
  %       but this distinctly doesn't bring the worker's perspective into the discussion;
  %       it projects an etic view, rather than attempts to understand from an emic view.
  %       then again, this was a time before Boas and Malinowski, so maybe this is natural.
  %       \cite{riisOtherSideLives,clark1908cotton}.
  % \item
          The primary avenue for workers to interact with requesters or managers has been through
        laborer advocacy groups, which later became guilds, unions, etc\dots
        and through that lens, there's a lot of research on
        the relationships between workers and requesters
        \cite{levi2009union,ahlquist2013interest,
              mccallum2013global,jacoby1983union}.
        One component of collectively negotiating with managers has been the process
        of collective action, a topic which has been substantively explored
        but is not quite yet answered
        \cite{russell1982collective,olsonlogic}.
  % \item
  this is harder; crowd work research doesn't just benefit from
        digitally mediated technology allowing us to make
        relationship networks like \citeauthor{crowdcollab} did;
        we also benefit from what we consider modern Anthropology and ethnography,
        something which fundamentally didn't exist or was still in its infancy during piecework's life.
        Still, we can look at primary sources, like \cite{american1921problem} by
        the president of the American Federation of Labor,
        to give us some hint of how they related to each other
        \cite{american1921problem,crowdcollab}.
% \end{enumerate}

\subsubsubsection{\whatchanged}
\topic{The differences between crowd workers and pieceworkers seem defined largely by
the differences in the places of work.}
Whereas it arguably became inevitable that workers would have a place to
meet, discuss, and collaborate
when they began sharing places of work,
online spaces make it much harder to do so.
Crowd workers can ``lurk'' and do tasks, or just do the occasional one--off task,
without any affiliation with
--- or even knowledge of ---
communities of peers
\ali{multiple citations that labor unions came out of factories here}
\cite{miller2011understanding,mcinnis2016one,earl2011digitally}.

While the historical management of workers had to be done by hiring a foreman,
who necessarily had an intuitive
--- perhaps sympathetic ---
relationship with workers,
the foreman of the \nth{20} century has largely been replaced
by the algorithm of the \nth{21} century
\cite{uberAlgorithm}.
The result of this change is that the agents managing work are now
cold and logical, if unforgiving.
Where a person might recognize that the ``attention check'' questions 
proposed by \citeauthor{le2010ensuring} ensure that malicious and inattentive are stopped,
some implementations of these approaches
(\cite[see][]{MaliciousCrowdworkersGadiraju}
only seem to antagonize workers
\cite{le2010ensuring,MaliciousCrowdworkersGadiraju}

@@

% \paragraph[relationships to work]{Relationships to work}\label{ch:workRelationship}
% \topic{A number of ethical questions surrounding the
% increasing complexity of crowd work have arisen in recent years.}
% \citeauthor{professionalcrowdworkEthics} bring some of these issues to light
% --- working for increasing amounts of time on tasks of growing complexity%
% , only to discover that requesters are not willing to pay%
% , for instance ---
% but these and other dangers range an enormous landscape
% \cite{professionalcrowdworkEthics}.
% \citeauthor{crowdworkFuture}
% list a few of the problems they identified in \citeyear{crowdworkFuture}
% --- motivation, feedback, reputation, quality control, to name a few ---
% while others discuss challenges such as fostering collective action
% and the opportunity for learning and career advancement
% \cite{crowdworkFuture,nickerson2013crowd,dynamo}.

% Some research already looks at research such as investing in workers, and
% informally, we know that this happens among industry requesters
% \cite{jonBrelig,shepherdingDow}.
% AMT, meanwhile, offers requesters the ability to create tasks which are
% not just hidden from unqualified workers by default, but completely.
% Requesters have taken to using lists of worker IDs which reference
% workers who have proven their reliability,
% representing a sort of proto--organization of loosely connected workers.

% \subsubsubsection{\pieceworkpers}
% The rise of labor unions in the \nth{20} century seems to have been precipitated by
% egregiously unjust conditions imposed on workers in factories and elsewhere
% \cite{ebbinghaus1999institutions}.
% Incidents broadly describing this dynamic can be found in research on AMT
% \cite{turkopticon,dynamo}.
% If these are prototypical labor advocacy organizations of contemporary on--demand work,
% the next question we should look to is if
% --- and indeed \textit{how} ---
% these institutions might face challenges in the future.

% For insight on this, we return to \citeyear{levi2009union}'s study of labor unions,
% and identify that
% ``Scholars who evaluate union governance by procedural criteria generally find that oligarchy tends to arise and persist even when democratic procedures are in place''
% \cite{levi2009union}.
% Indeed, \citeauthor{levi2009union} writes about the general perception that labor unions were either
% This perception already appears to be emerging in digitally mediated peer--governed organizations,
% as \citeauthor{keegan2010egalitarians} and others have illustratively documented
% \cite{beschastnikh2008wikipedian,keegan2010egalitarians}.
% If these organizations and others are to avoid the same fate that labor unions faced,
% they should take care to study this phenomenon and attempt to avoid it.

% \subsubsubsection{\whatchanged}
% \topic{While online and distributed workers can be harder to find,
% other features make the study thereof rewarding for the substantively different ways
% that we can approach their study.}
% The longitudinal analysis of everyday discourse, for instance,
% is trivial in the study of online communities

% \subsubsubsection{\implication}
